Marine species do not need visas: the transboundary nature of the world’s exploited marine species

### 2020-05-03 Scripts/Manuscript_Draft.Rmd
Fixed supplement references

Finally, the results of this study only considered those species that had a *Species Index* of 1 (e.g. all datasets agree on presence) and at least 25% of *Area Index* (e.g. the species shared distribution was at least 25% in each EEZ). This presents a relative conservative estimate of the number of transboundary species in the world. However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Figure \@(fig:CallSup2)).

@@

Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Figure \@(fig:CallSup1)). Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production. Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp]. Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA celebrating a management agreement with the latter over the Berring Sea since 1988 [@NOAA:gX6CtUTk]. Transboundary species also contribute largely to fisheries in E. Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05). Particularly, China the world's top fish producer [@FAO:2018KK] getting one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons). Differences in transboundary fisheries can also be illustrated in terms of catch-revenue/EEZ $km^2$ (Figure \@ref(fig:CallFigure2)). As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table \@ref(tab:TabSup2)), however, it has the most revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).

@@

The number of gridcells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary. Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Figure \@(fig:Call-Sup-2)). As expected, using a more relaxed value (e.g. the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4. The current analysis utilized a 25% *Area Index* threshold (Figure \@(fig:CallSup2) darker histogram).

>>>>

Finally, the results of this study only considered those species that had a *Species Index* of 1 (e.g. all datasets agree on presence) and at least 25% of *Area Index* (e.g. the species shared distribution was at least 25% in each EEZ). This presents a relative conservative estimate of the number of transboundary species in the world. However, using a different *Species Index* will give results based on less datasets while a smaller *Area Index* will estimate more transboundary species (Figure \@ref(fig:CallSup2)).

@@

Peru and Russia, responsible for the two largest fisheries in the world [@FAO:2018KK], lead transboundary catch statistics harvesting over 5.8 million tons annually each on average between 2005 and 2014 (Figure \@ref(fig:CallSup1)). Peru's catches are mainly composed of Peruvian anchoveta (*Engraulis ringens*), shared with Chile, and account for 79% of the transboundary species production. Recently these two countries have signed an agreement to work towards standardized stock assessments through coordinated management of this species [@UNDP:2016wp]. Similarly, Russia shares the Alaskan pollock (*Theragra chalcogramma*) fishery with both Japan and the USA celebrating a management agreement with the latter over the Berring Sea since 1988 [@NOAA:gX6CtUTk]. Transboundary species also contribute largely to fisheries in E. Asia (one-way ANOVA; *Df*(16,158) = 2.265, *p* = 0.005, $\alpha$ = 0.05). Particularly, China the world's top fish producer [@FAO:2018KK] getting one third (5.1 million tons) of the total catches from transboundary species, followed by Japan (1.8 million tons) and South Korea (1.06 million tons). Differences in transboundary fisheries can also be illustrated in terms of catch-revenue/EEZ $km^2$ (Figure \@ref(fig:CallFigure2)). As an example, the aggregated area of all EEZs of Northern Europe is 3.3 million $Km^2$, the $5^{th}$ smallest of the 17 groups analyzed (Table \@ref(tab:TabSup2)), however, it has the most revenue (USD 246.7 million per $Km^2$) and catch (260.1 tons per $Km^2$) of transboundary species per EEZ area, but only significantly differing from Sub-Saharan African and Southern Europe countries (*p* < 0.05).

@@

The number of gridcells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary. Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Figure \@(fig:Call-Sup-2)). As expected, using a more relaxed value (e.g. the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4. The current analysis utilized a 25% *Area Index* threshold (Figure \@ref(fig:CallSup2) darker histogram).
